Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-21 manuscript/manuscript.Rmd
Updated .get_transformation_parameters
Update residual data.
Final analyses of the main manuscript.

Figure \ref{fig:optimised-weighting-function-parameters} shows the distribution of errors $\left| \hat{\lambda}^r - \hat{\lambda}_0 \right|$ for non-robust transformations, as well as robust transformations using the optimal weighting function parameters. In the presence of outliers on either side of the distribution, the Yeo-Johnson transformation yields smaller errors than the Box-Cox transformation. For both transformations, weighting based on empirical probabilities yields the most consistent $\lambda$ parameter estimates in the presence of outliers. Weighting based on residual errors tended to perform least well, and were generally similar to (Yeo-Johnson) or worse than (Box-Cox) non-robust transformations.

@@

\midrule
0.042 & 0.063 & 0.077 & 0.090 & 0.106 & 0.118 & 0.159 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

@@

```{r top-gear, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2}
cap <- paste0(
  "Quantile-quantile plots for the fuel consumption data in the Top Gear dataset. ",
  "This data contains three strong outliers for highly efficient vehicles. ",
  "The left panel shows the quantile-quantile plot for the original data. ",
  "The middle panel shows the quantile-quantile plots for data transformed using ",
  "the original Yeo-Johnson transformation, and Raymaekers and Rousseeuw's robust adaptation \cite{Raymaekers2021-kq}. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.58$, respectively. ",
  "The right panels shows the quantile-quantile plots for data transformed using ",
  "the non-robust and robust shift-sensitive transformations. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.36$, respectively. ",
  "Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses."
)

@@

```{r housing-data, warning=FALSE, message=FALSE, fig.cap=cap, fig.height=2}
cap <- paste0(
  "Quantile-quantile plots for the fuel consumption data in the Top Gear dataset. ",
  "This data contains three strong outliers for highly efficient vehicles. ",
  "The left panel shows the quantile-quantile plot for the original data. ",
  "The middle panel shows the quantile-quantile plots for data transformed using ",
  "the original Yeo-Johnson transformation, and Raymaekers and Rousseeuw's robust adaptation [@Raymaekers2021-kq]. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.58$, respectively. ",
  "The right panels shows the quantile-quantile plots for data transformed using ",
  "the non-robust and robust shift-sensitive transformations. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.36$, respectively. ",
  "Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses."
)

.plot_sacramento_house_prices(
  plot_theme = plot_theme
)
```

>>>>

Figure \ref{fig:optimised-weighting-function-parameters} shows the distribution of errors $\left| \hat{\lambda}^r - \hat{\lambda}_0 \right|$ for non-robust transformations, as well as robust transformations using the optimal weighting function parameters. In the presence of outliers on either side of the distribution, the Yeo-Johnson transformation yields smaller errors than the Box-Cox transformation. For both transformations, weighting based on empirical probabilities yields the most consistent $\lambda$ parameter estimates in the presence of outliers. Other methods did not outperform the non-robust power transformation method.

@@

\midrule
0.041 & 0.062 & 0.075 & 0.088 & 0.103 & 0.115 & 0.154 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
```

@@

```{r top-gear, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Quantile-quantile plots for the fuel consumption data in the Top Gear dataset. ",
  "This data contains three strong outliers for highly efficient vehicles. ",
  "The left panel shows the quantile-quantile plot for the original data. ",
  "The middle panel shows the quantile-quantile plots for data transformed using ",
  "the original Yeo-Johnson transformation, and Raymaekers and Rousseeuw's robust adaptation \\cite{Raymaekers2021-kq}. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.58$, respectively. ",
  "The right panels shows the quantile-quantile plots for data transformed using ",
  "the non-robust and robust shift-sensitive transformations. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.36$, respectively. ",
  "Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses."
)

@@

```{r housing-data, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Quantile-quantile plots for the fuel consumption data in the Top Gear dataset. ",
  "This data contains three strong outliers for highly efficient vehicles. ",
  "The left panel shows the quantile-quantile plot for the original data. ",
  "The middle panel shows the quantile-quantile plots for data transformed using ",
  "the original Yeo-Johnson transformation, and Raymaekers and Rousseeuw's robust adaptation [@Raymaekers2021-kq]. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.58$, respectively. ",
  "The right panels shows the quantile-quantile plots for data transformed using ",
  "the non-robust and robust shift-sensitive transformations. ",
  "For these, the empirical central normality test yields $p=0.01$, and $p=0.36$, respectively. ",
  "Samples with observed quantiles below $-3.0$ or above $3.0$ are indicated by crosses."
)

.plot_sacramento_house(
  plot_theme = plot_theme
)
```
